Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-22 paper.tex
added dask summary -- to be fixed

    \section{Geneflow} 
        \subsection{Pipeline description} 
        \subsection{Pipeline execution} 
        \subsection{Debugging and provenance} 
    \section{Toil}
        \note{obtained from paper's supplementary documentation}
        Toil is another general workflow framework aimed at the processing of 
        scientific big data, with its main focus being on genomics workflows. It 
        prides itself in not only its ability to not only scale the processing 
        of very large datasets, but also its portability, allowing it to be 
        executed on any environment. Toil pipelines can be written in CWL, WDL 
        (Workflow Description Language) and Python. The Toil workflow 
        framework is also open-sourced, making it a community-driven effort. 
        \note{as is the case with most}

@@

        A few extensions have also been added to the library in order to improve
        user experience. An important extension is the introduction of a
        \textit{combiner}, which enables the commutative and associative reduce
        function to be applied to the same keys on the hosts where the
        \textit{map} task was executed. Like the \textit{map} task, the
        \textit{combiner} produces intermediate output which is sent to the
        \textit{reducer}. This alleviates the amount of key-value pairs that
        must be transferred over the network from the map host to the reduce
        host, and as a result, improves performance. Other extensions include
        the ability to create user-defined partitioning functions, a guaranteed
        increasing key sort order, the ability for the user to specify input
        types, an option to skip records that continuously result in execution
        failure, the ability to produce auxiliary output files in \textit{map}
        or \textit{reduce} task, live status updates stream to HTTP server, the
        ability to run all code on a single local machine, and a
        \textit{Counter} class.  \section{spark} \begin{itemize} \item based on
        map-reduce \item in-memory processing \item lazy evaluation \item
        general framework \end{itemize}

@@

>>>>

    \section{Galaxy}
        Galaxy is another open-source genomics web-platformed designed to 
        address the
        reproducibility crisis in genomics in addition to facilitating workflow
        creation process for non-programmers and ensuring the transparency of 
        the workflows. It differs from workflow engines in that it is a full
        platform designed for researchers to create and share their workflows
        and data with the community. Building workflows in Galaxy is
        entirely GUI-based enabling users with little to no programming
        knowledge to build workflows. Metadata is extracted from the workflows
        during executions and pipelines can be annoted and shared with other 
        users.

        \subsection{Pipeline description}
        In order to make workflow creation accessible to researchers with little
        -to-no programming skills, Galaxy provides a GUI. 
        The GUI allows users to drag-and-drop CLI tools to the screen to create
        workflows. In order for new tools to be added to Galaxy, the user must 
        write a configuration file which contains details on input and output
        specifications and how to execute the tool. During workflow creation, 
        the workflow editor will determine if the inputs and outputs of 
        connected tools are compatible.

        Alternatively, users may also create workflows by editing workflows that
        have been published to Galaxy or using their own analysis history to 
        generate a workflow. Any workflow created by a user can be published to
        the Galaxy server and made available to all other users.

        \note{no details on workflow failure}
        As Galaxy is meant to be easy-to-use for researchers, all that is 
        required to execute pipelines is access to their webpage. Users have 
        access to detailed records of the executed workflow's metadata and 
        provenance indicating the outcome of the executed workflow.

        Should users desired to host their own Galaxy server, it is possible to
        install Galaxy locally, on HPC with SLURM or PBS installed or the cloud.

        \subsection{Debugging and provenance} 
        Provenance is a big part of Galaxy as it aims to improve accessibility, 
        reproducibility and transparency of workflows. During workflow execution
        , Galaxy automatically produces metadata for each of the workflow tasks.
        This metadata includes details on the input and output datasets, tools 
        user and parameter values.

        In addition to Galaxy's metadata capture, it is also possible for the 
        user to annotate and tag their workflow. This enables the user to 
        communicate with others the intent of the analysis steps in addition to 
        incorporating search capabilities to their workflows.

        Galaxy also provides the Pages capability. Pages is a web-based document
        that enables users to automatically generate detailed documentation of 
        their analyses.

    \section{Toil}
        \note{obtained from paper's supplementary documentation}
        Toil is another general workflow framework aimed at the processing of 
        scientific big data, with its main focus being on genomics workflows. It 
        prides itself in not only its ability to not only scale the processing 
        of very large datasets, but also its portability, allowing it to be 
        executed on any environment. Toil pipelines can be written in CWL, WDL 
        (Workflow Description Language) and Python. The Toil workflow 
        framework is also open-sourced, making it a community-driven effort. 
        \note{as is the case with most}

@@

        A few extensions have also been added to the library in order to improve
        user experience. An important extension is the introduction of a
        \textit{combiner}, which enables the commutative and associative reduce
        function to be applied to the same keys on the hosts where the
        \textit{map} task was executed. Like the \textit{map} task, the
        \textit{combiner} produces intermediate output which is sent to the
        \textit{reducer}. This alleviates the amount of key-value pairs that
        must be transferred over the network from the map host to the reduce
        host, and as a result, improves performance. Other extensions include
        the ability to create user-defined partitioning functions, a guaranteed
        increasing key sort order, the ability for the user to specify input
        types, an option to skip records that continuously result in execution
        failure, the ability to produce auxiliary output files in \textit{map}
        or \textit{reduce} task, live status updates stream to HTTP server, the
        ability to run all code on a single local machine, and a
        \textit{Counter} class.

    \section{spark} \begin{itemize} \item based on
        map-reduce \item in-memory processing \item lazy evaluation \item
        general framework \end{itemize}

@@

        \section{Dask}
        Dask contains three primary abstractions: the \textit{dask.array}, 
        \textit{dask.bag} and \textit{dask.dataframe}. The \textit{dask.array} 
        is an abstraction that enables parallel NumPy-like operations using task
        scheduling. It can additionally be used on data that does not fit in 
        memory. The \textit{dask.array} used blocked array algorithms to break 
        down large commonly-used linear algebra functions into smaller ones that
        can be partially parallelized.

        Dask array functions all create an \textit{Array} object which contains 
        the dask graph \textit{.dask}, details on the overall shape and the 
        shape of each subdivided portion (chunk) of the array (\textit{.chunks})
        , the \textit{.name} representing which keys map to the results, and the
        data type.

        A limitation of the Dask array is that it must know the shape of the 
        array at graph creation time.

        The Dask bag is similar to that of a Python list, however, order cannot 
        be guaranteed. As Dask bags typically operate on Python objects, 
        performance is bound by the Global Interpreter Lock (GIL), therefore 
        multiprocessing schedulers must be used instead of multithreading ones.

        The Dask bag contains functions like \textit{map} and \textit{filter}, 
        in addition to many other functions that can be found in the PyToolz API
        . It is particularly well suited for the handling of data dumps.

        The Dask dataframe consists of a collection of Pandas DataFrames, and 
        thus implements many of the functionalities found in an Pandas DataFrame
        . The dataframe is well suited for running on partioned datasets, where 
        partitions are clearly defined by an index.

        In order to execute the Dask graphs in an efficient manner, proper 
        scheduling is required. Dask uses dynamic scheduling for all their 
        schedulers. When a worker reports completion of a task, the runtime 
        state is updated to reflect that the task has been completed, tasks that
        can now be executed are marked and the data which can be released is 
        determined. To ensure that workers complete execution of related tasks 
        before commencing unrelated ones, a \textit{last in first out} policy is
        used. As Dask graphs are entirely decoupled from the scheduler that they
        use, Dask users are free to design their own scheduler that best suits 
        their needs.
